### 2020-06-09 inst/jss/kane-listdown/kane-listdown.Rmd
JSS Initial commit.

---
title: Programmatic Generation of R Markdown Documents with \pkg{listdown}
author:
  - name: Michael Kane
    affiliation: Yale University
    address:
    - 60 College Street
    - New Haven, CT 06510, USA
    email:  michael.kane@yale.edu
abstract: >
  An abstract of less than 150 words.
preamble: |
  % Any extra LaTeX you need in the preamble
output: rticles::rjournal_article
---

>>>>

---
documentclass: jss
author:
  - name: Michael Kane
    affiliation: Yale University
    address:
    - 60 College Street
    - New Haven, CT 06510, USA
    email:  michael.kane@yale.edu
title:
  formatted: "On the Programmatic Generation of Reproducible Documents"
  # If you use tex in the formatted title, also supply version without
  plain:     "On the Programmatic Generation of Reproducible Documents"
  # For running headers, if needed
  short:     "Programmatic Generation of Reproducible Documents"
abstract: >
  The abstract of the article.
keywords:
  # at least one keyword must be supplied
  formatted: [reproducibility, data presentation]
  plain:     [reproducibility, data presentation]
preamble: >
  \usepackage{amsmath}
output: rticles::jss_article
---
